{\fontfamily{ptm}\selectfont The Proximal Point interpretation of Nesterov accelerated proximal gradient}

### 2024-08-26 Notebook LaTEX/Momentum Accelerations/paper.tex
>w<, changes to the notes

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    As a major extension, our work describes the method of proximal gradient using the PPM interpretations. We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof. Finally, we derive major variants of the accelerated gradient and find the match of the stepsize parameters in the PPM form. 
    \par
    Classical analysis and extension of Nesterov accelerated gradient exist in the literatures. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and cherry picked Nesterov's estimating sequence to assist the proof for the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since it doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm however, lead to the valuable insights that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function.

@@

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth. 
    \end{assumption}

@@

            h(x^+) + \langle \mathcal G_L (x), z - x\rangle + 

@@

            g(z) + \langle \partial g(x^+), x^+ - z\rangle. 

@@

        Apply the above by considering the following sequence of relations

@@

                + (g(z) + \langle \partial g(x^+), x^+ - z\rangle)

@@

                (g(z) + \langle \partial g(x^+), x^+ - z\rangle)

@@

                    \langle \partial g(x^+), x^+ - z\rangle

@@

                \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 

@@

                    \langle \mathcal G_L(x), x^+ - z\rangle 

@@

                &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
                \underbrace{\langle L(x - x^+), x - z\rangle}_{
                    = - \langle \mathcal G_L (x), z - x\rangle
                - \frac{L}{2}\Vert x - x^+\Vert^2
            \end{aligned}. 

@@

    \begin{definition}[AG proximal gradient generic form]
    \label{def:ag_prox_grad_generic}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$.
        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
        $$
        \begin{aligned}
            y_t^+ &= \mathcal T_L(y_t)
            \\
            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
            \\
            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
            \\
            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
        \end{aligned}
        $$
        for all $t\in \mathbb N$. 
    \end{definition}
    \begin{remark}
        Observe that $z_{t + 1} = y_t^+$. 
    \end{remark}

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, which is the proximal gradient set, then the above expression simplifies to 
        $$
        y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.

    \begin{lemma}[Lyapunov Inequality]. 

@@

        Fix any $\bar x, x, \tilde\eta > 0$, define

@@

            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x. 

@@

            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2)
            &\quad \le 

@@

            \forall z':
            h(\mathcal T_L \bar x) - h(z') 

@@

        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, anchored at $\bar x$ by 

@@

        Directly observe that we have 

@@

        The convexity of $g$ yields: 

@@

                \partial g(z), z' - z

@@

            \langle \partial g(z), z - z'\rangle. 

@@

            \langle \nabla f(\bar x) + \partial g(z), z - z'\rangle + 

@@

        {lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        to give the desired results. 

@@

    \label{remark:upsilon-upperbound-for-iterates}

@@

        {definition \ref*{def:ag_prox_grad_generic}}.

@@

        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, 
        the results can be written as 

@@

            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2)

@@

            &\quad \le 

@@

            h(z_{t + 1}) - h(z_t) \le 

@@

        It will be used next. 

@@

    \begin{theorem}[Generic AG Convergence]

@@

        {remark \ref*{remark:upsilon-upperbound-for-iterates}}. 

@@

        {definition \ref*{def:ag_prox_grad_ppm}} 

@@

        \hyperref[thm:generic_ag_convergence]{theorem \ref*{thm:generic_ag_convergence}}

@@

        \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}) 

@@

        {remark \ref*{remark:upsilon-upperbound-for-iterates}}

@@

        {definition \ref*{def:ag_prox_grad_generic}}

@@

        {theorem \ref*{thm:generic_ag_convergence}}. 

@@

\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
    In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
    \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}, 
    we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
    \hyperref[thm:ag_generic_stepsize_constraints]
    {theorem \ref*{thm:ag_generic_stepsize_constraints}}
    and derive their convergence rate respectively.

    \subsection{Recovering FISTA} 
        Let $\epsilon_i$ be given by
        \hyperref[thm:ag_generic_stepsize_constraints]
        {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
        \begin{align*}
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            \right), 
            \\
            c_{t + 1} &= a_t^2. 
        \end{align*}
        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
        \begin{lemma}[Deriving Similar Triangle Form I]
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
            \hyperref[def:ag_prox_grad_generic]
            {definition \ref*{def:ag_prox_grad_generic}}
            simplifies into 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                \\
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                \\
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            \end{align*}
            It is also equivalent to 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \\
                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
            \end{align*}
            And this is the FISTA algorithm. 
        \end{lemma}

@@

            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}},

@@

            \hyperref[def:ag_prox_grad_generic]{definition \ref*{def:ag_prox_grad_generic}}

@@

            {theorem \ref*{thm:ag_generic_stepsize_constraints}}, 

@@

            \hyperref[thm:ag_generic_stepsize_constraints]{theorem \ref*{thm:ag_generic_stepsize_constraints}}

@@

            \hyperref[thm:generic_ag_convergence]{\ref*{thm:generic_ag_convergence}},

>>>>

\section{Introduction}
    Recent works from Ahn and Sra \cite{ahn_understanding_2022} and Nesterov \cite{nesterov_lectures_2018} inspired content in this section.
    Ahn and Sra explored the interpretation of Nesterov acceleration as the proximal point method (PPM) applied to an upper surrogate function, and then a lower surrogate function. 
    Inspired by the interpretation, we generalize the framework to the case of $h = f + g$ with $f$ Lipschitz smooth and $g$ convex whose proximal mapping can be evaluated exactly for algorithm implementations. 
    As a major extension, our work describes the method of proximal gradient using the PPM interpretations. We also compactify the Lypunov analysis with the introduction of an error terms for the convergence proof. Finally, we derive major variants of the accelerated gradient(AG) and find the match of the stepsize parameters in the PPM form. 
    \par
    Some of the earlier examples for the extension of the Nesterov acceleration method make use of the classical analysis introduced by Nestrov. 
    It uses the Nesterov acceleration sequence. 
    See \cite{guler_new_1992} for an extension of the Nesterov accelerated gradient method to the proximal point method for convex programming. 
    However the classical analysis found in \cite[chapter 2]{nesterov_lectures_2018} involves the assumption of a specific kind of Lypunov function and a specific format of the Nesterov's estimating sequence to accomodate the proof for the relations between the parameters in the algorithm. 
    In Ahn's work however, the complexities are packaged into the proximal point interpretation of accelerated gradient. 
    It uses a lemma from Moreau envelope to derive the Lypunov analysis, the sizes, and parameters for several variants of the algorithm. 
    \par
    Numerous notable variations of Nesterov accelerated gradient exists. \cite[(6.1.19)]{nesterov_lectures_2018} described a variant of accelerated gradient restricted to a convex domain $Q$. 
    Beck and Toubolle \cite{beck_fast_2009} introduced a variant the problem type of smooth plus non-smooth, known as FISTA. 
    For a variant of accelerated gradient where the iterates converge, see \cite{chambolle_convergence_2015}. 
    Extension such as the Harpen acceleration for the resolvent operator in general is outside of the scope since it doesn't have a Moreau envelope. 
    \par
    A wide varieties of interpretation for the Nesterov accelerated gradient exist in the literatures. 
    Consult \cite{su_differential_2015} for a dynamical system interpretation of Nesterov acceleration. 
    The dynamical system interpretation of the algorithm leads to the valuable insight that restarting the accerlated gradient algorithm would lead to faster convergence rate for the class of strongly convex function. 
    In work by \cite{allen-zhu_linear_2016}, they interpreted the idea of Nesterov acceleration as a combinations of gradient descent and mirror descent.

@@

\section{Preliminaries}\label{sec:preliminaries}
    In this section we introduce the a descent lemma for Proximal Point Method (PPM) in the convex case. 
    We define the proximal gradient mapping $\mathcal T_L$, and gradient mapping $\mathcal G_L$ for function satisfying 
    \hyperref[assumption:smooth-nonsmooth-sum]
    {assumption \ref*{assumption:smooth-nonsmooth-sum}}. 
    A lower bound function is identified using the gradient mapping operator and proved in
    \hyperref[lemma:grad_map_linearization]{Lemma \ref*{lemma:grad_map_linearization}}, 
    this is a key component of the proximal point interpretation of the accelerated gradient method. 
    \begin{assumption}\label{assumption:smooth-nonsmooth-sum}
        Let $h = f + g$ where $f, g$ are convex and $f$ is Lipschitz-Smooth with constant $L$. 
    \end{assumption}

@@

            h(x^+) + 
            \langle \mathcal G_L (x), z - x\rangle 

@@

            g(z) + \langle v, x^+ - z\rangle\quad 
            \forall v \in \partial g(x^+)

@@

        For all $v \in \partial g (x^+)$, apply the above by considering the following sequence of relations

@@

                + (g(z) + \langle v, x^+ - z\rangle)

@@

                (g(z) + \langle v, x^+ - z\rangle)

@@

                    \langle v, x^+ - z\rangle

@@

                \langle \nabla f(x) + v, x^+ - z\rangle 

@@

            % \\& 
            % \begin{aligned}
            %     &= h(z) + 
            %         \langle \mathcal G_L(x), x^+ - z\rangle 
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     + \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}
            % \\& 
            % \begin{aligned}
            %     &= h(z) + \langle L(x - x^+), x^+ - x + x - z\rangle 
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     + \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}
            % \\&
            % \begin{aligned}
            %     &= h(z) + 
            %     \underbrace{\langle L(x - x^+), x - z\rangle}_{
            %         = - \langle \mathcal G_L (x), z - x\rangle
            %     }
            %     - \frac{\mu}{2}\Vert z - x\Vert^2
            %     - \frac{L}{2}\Vert x - x^+\Vert^2
            % \end{aligned}
        Showed in  
        \hyperref[lemma:grad-map-approx-subgrad]{Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        we have $\mathcal G_L(x) \in \nabla f(x) + \partial g(x^+)$, choose $v \in \partial g(x^+)$ such that $G_L(x) = \nabla f(x) + \partial g(x^+)$, it yields
            h(x^+) & 
            \le h(z) + 
            \langle \nabla f(x) + v, x^+ - z\rangle 

@@

@@

    \begin{definition}[AG proximal gradient generic form]
    \label{def:ag_prox_grad_generic}
        Define $\eta_t, \tilde \eta_t$ to be $> 0$ for all $t \in \N$. 
        With initial iterate $x_0, y_0$.
        The generic form has iterates $(y_t, x_{t + 1}, z_{t + 1})$ such that 
        $$
        \begin{aligned}
            y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
            \\
            x_{t + 1} &= x_t - \tilde \eta_{t + 1} \mathcal G_L(y_t)
            \\
            z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
        \end{aligned}
        $$
        for all $t\in \mathbb N$. 
    \end{definition}
    \begin{remark}
        Observe that $z_{t + 1} = y_t^+$. 
    \end{remark}

    \begin{proposition}
    \label{prop:derive_ag_prox_grad_tript}
       We have equalities
        \begin{align*}
            x_{t + 1} &= \argmin_{x}
            \left\lbrace
                l_h(x, y_t) + \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
            \right\rbrace
            \\
            &= x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t), 
            \\
            y_{t + 1} &= \argmin_{x}
            \left\lbrace
                    h(y_t^+) + \langle \mathcal G_L(y_t), x - y_t\rangle + \frac{L}{2}\Vert x -y_t\Vert^2 + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &= (1 + L\eta_{t + 1})^{-1}
            (x_{t + 1} + L\eta_{t + 1}(y_t - L^{-1}\mathcal  G_L(y_t))). 
        \end{align*}
        This thows
        \hyperref[def:ag_prox_grad_ppm]{Definition \ref*{def:ag_prox_grad_ppm}}
        and 
        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}} 
        are equivalent. 
    \end{proposition}
    \begin{proof}
        Let $y_t^+ = \mathcal T_L(y_t)$, recall that $l_h(x; y_t) = h(y_t^+) + \langle \mathcal G_L(y_t), x -y_t\rangle \le f(x)$ by 
        \hyperref[lemma:grad_map_linearization]
        {Lemma \ref*{lemma:grad_map_linearization}}
        Since $l_h(x; y_t)$ is a simple linear function wrt $x$, minimizing the quandratic where to get $x_{t + 1} = x_t - \tilde\eta_{t + 1} \mathcal G_L(y_t)$; for $y_{t + 1}$, complete the square on the second and the third terms: 
        \begin{align*}
            & \frac{L}{2}\left(
                2\langle L^{-1}\mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= 
            \frac{L}{2}
            \left(
                - \Vert L^{-1} \mathcal G_L(y_t)\Vert^2  
                + \Vert L^{-1} \mathcal G_L(y_t)\Vert^2 
                + 
                2\langle L^{-1} \mathcal G_L(y_t), x - y_t\rangle + 
                \Vert x - y_t\Vert^2
            \right)
            \\
            &= \frac{L}{2}\left(
                - \Vert L^{-1}\mathcal G_L(y_t)\Vert^2  
                + \Vert x - (y_t - L^{-1}\mathcal G_L(y_t))
                \Vert^2
            \right), 
        \end{align*}
        therefore it transforms into 
        \begin{align*}
            y_{t + 1} &=\argmin_{x} \left\lbrace
                \frac{L}{2}\left\Vert 
                    x - (y_t - L^{-1}\mathcal G_L(y_t))
                \right\Vert^2
                + \frac{1}{2\eta_{t + 1}}\Vert x - x_{t + 1}\Vert^2
            \right\rbrace
            \\
            &=
            \frac{
                \left(y_t - L^{-1}\mathcal G_L(y_t)\right) + x_{t + 1}
            }{L + \eta_{t + 1}^{-1}}.
        \end{align*}
        Define $z_{t + 1} = y_t - \mathcal G_L(y_t) = \mathcal T_L(y_t)$, then the above expression simplifies to 
        $$
            y_{t + 1} = (1 + L\eta_{t +1})^{-1}(x_{t + 1}+ L\eta_{t + 1}z_{t + 1}). 
        $$
    \end{proof}
    \begin{remark}
        $y_{t + 1}$ is the minimizer of a simple quadratic. 
        Given that the original function $h$ is potentially non-smooth, therefore it's not always an upper bound of $h(x)$. 
        The upper bound interpretation of the smooth case as proposed by Ahn \cite{ahn_understanding_2022}, Sra for the update of $y_{t + 1}$ fails when $h$ is non-smooth! 
    \end{remark}

\section{Generic Lyapunov analysis for accelerated gradient via PPM}
\label{sec:generic_ag_ppm_lyapunov_analysis}
    In this section we derive the generic convergence rate formuated by $\eta_i, \tilde \eta_i$. 
    \par
    The Lypunov function in 
    \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}}
    is identical to Ahn and Sra 
    \cite[section 4.2]{ahn_understanding_2022}, 
    except for the involvement of the gradient mapping. 
    We adapated it into the context of proximal gradient by 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}}
    \par
    We present the convergence rate by compatifying results into 
    \hyperref[lemma:nsmooth_agg_lyapunov_upper_bound]
    {Lemma \ref*{lemma:nsmooth_agg_lyapunov_upper_bound}} 
    to assist the proof of  
    \hyperref[thm:generic_ag_convergence]
    {Theorem \ref*{thm:generic_ag_convergence}} 
    which states new results that are extension to Ahn and Sra's works by introducing an error term to the Lypunov analysis, allowing for a weaker constraints for the stepsize paramters $\tilde \eta_i, \eta_i$ from 
    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}. 
    \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    states the weakened constraints on the stepsize parameters $\tilde \eta_i, \eta_i$. 
    \par
    Throughout the section, we continue the assumption for $h = f + g$, gradient mapping $\mathcal G_L$ and proximal gradient mapping $\mathcal T_L$ from the previous section.

    \begin{lemma}[Lyapunov inequality]

@@

        Fix any $\bar x, x, z',\tilde\eta > 0$, define

@@

            \hprox_\phi(x) = x - \tilde \eta\mathcal G_L \bar x,
            \frac{1}{2}(\Vert x^+ - x_*\Vert^2 - \Vert x - x_*\Vert^2), 
            h(\mathcal T_L \bar x) - h(z'). 

@@

            \Upsilon_1 &\le 

@@

            \Upsilon_2 &\le 

@@

        Function $\phi$ is a linear function that qualifies as a lower bound of $\tilde \eta h$, at $\bar x$ by 

@@

        Observe that we have 

@@

        The convexity of $g$ yields for all $v \in \partial g(z)$: 

@@

                v, z' - z

@@

            \langle v, z - z'\rangle. 

@@

            \langle \nabla f(\bar x) +v, z - z'\rangle + 

@@

        {Lemma \ref*{lemma:grad-map-approx-subgrad}}, 
        there exists $v \in \partial g (\mathcal T_L(\bar x))$ such that $\mathcal G_L(\bar x) = \nabla f(z) + v$, hence the theorem is proved. 

@@

    \begin{remark}\label{remark:upsilon-upperbound-for-iterates}

@@

        {Definition \ref*{def:ag_prox_grad_generic}}.

@@

        Set $z' = z_t, \tilde \eta = \tilde \eta_{t + 1}$, we define the quantities: 

@@

            \frac{1}{2}(\Vert x_{t + 1} - x_*\Vert^2 + \Vert x_t - x_*\Vert^2),

@@

            h(z_{t + 1}) - h(z_t). 
        It then produces the inequalities: 

@@

@@

        This is useful for the convergence proof of the algorithm. 

@@

    \begin{theorem}[Generic AG convergence]

@@

        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}. 

@@

        {Definition \ref*{def:ag_prox_grad_ppm}} 

@@

        {Theorem \ref*{thm:generic_ag_convergence}}

@@

        \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}) 

@@

        {Remark \ref*{remark:upsilon-upperbound-for-iterates}}

@@

        {Definition \ref*{def:ag_prox_grad_generic}}

@@

        {Theorem \ref*{thm:generic_ag_convergence}}. 

@@

\section{Recovering existing variants of Nesterov accelerated gradient}\label{sec:recovery}
    In this section, we recovers several variants of the accelerated gradient in the literatures as a special case of 
    \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}, 
    we sate the choice of stepsize parameter $\eta_i, \tilde \eta_i$, verify that they satisfies 
    \hyperref[thm:ag_generic_stepsize_constraints]
    {Theorem \ref*{thm:ag_generic_stepsize_constraints}}
    and derive their convergence rate respectively.

    \subsection{Recovering FISTA} 
        Let $\epsilon_i$ be given by
        \hyperref[thm:ag_generic_stepsize_constraints]
        {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 
        setting $\epsilon_i = 0$ for all $i$ yields $a_t = 1 + L\eta_t = \tilde \eta_{t + 1}$, for all $t \in \N$ where $a_t$ produces the relations 
        \begin{align*}
            a_{t + 1} &= (1/2)\left(
                1 + \sqrt{1 + 4 c_{t + 1}}
            \right), 
            \\
            c_{t + 1} &= a_t^2. 
        \end{align*}
        The recurrenct relations of $a_t$ indicates that it's the famous Nesterov momentum sequence. 
        In this case, there exists a momentum form of the generic form and it reduces to FISTA from Beck and Toubolle \cite{beck_fast_2009-1}. 
        The following lemma uses $a_t$ to establish equivalence between the generic form of the algorithm and FISTA, a specific variant of accelerated gradient method. 
        \begin{lemma}[Deriving Similar Triangle Form I]
            \quad \\
            With the choice of stepszie $\tilde \eta_{t + 1} = \eta_t + L^{-1}$,
            \hyperref[def:ag_prox_grad_generic]
            {Definition \ref*{def:ag_prox_grad_generic}}
            simplifies into 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1} \mathcal G_L(y_t)
                \\
                x_{t + 1} &= z_{t + 1} + L\eta_t (z_{t + 1} - z_t)
                \\
                y_{t + 1} &= 
                (1 + L\eta_{t + 1})^{-1}
                (
                x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                ). 
            \end{align*}
            It is also equivalent to 
            \begin{align*}
                z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \\
                y_{t + 1} &= z_{t + 1} + (1 + L\eta_{t + 1})^{-1}L\eta_t (z_{t + 1} - z_t). 
            \end{align*}
            And this is the FISTA algorithm. 
        \end{lemma}

@@

            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}},

@@

            \hyperref[def:ag_prox_grad_generic]{Definition \ref*{def:ag_prox_grad_generic}}

@@

            {Theorem \ref*{thm:ag_generic_stepsize_constraints}}, 

@@

            \hyperref[thm:ag_generic_stepsize_constraints]{Theorem \ref*{thm:ag_generic_stepsize_constraints}}

@@

            \hyperref[thm:generic_ag_convergence]{Theorem \ref*{thm:generic_ag_convergence}},
